The Evolution of Manufacturing Ecosystem in Cloud Manufacturing Architecture

### 2016-09-08 design.tex
draft for cfp

\subsubsection{Assumptions} % (fold)
\label{ssub:assumptions_nomenclature}
To scope our research, we make some assumptions as follows:
\begin{compactitem}
\item Each single task should be assembled by its task-parts, and these parts should be processed simultaneously;
\item The quality of product is determined by the worst quality of the selected resource;
\item Resource are renewable that the available capacity will be return to when the process procedure finished;
\item Resource quality comply normal distribution with given mean and standard deviation by provider when registered;
\item Cooperate and process procedure cannot be interrupted;
\item Provider can only schedule task-parts in inactive status. 
\end{compactitem}
These assumptions are suitable for the original mode, while in other extension, some of the assumptions will be modified.

@@

$(i,j,k,l,\alpha)$. when in schedule procedure, we omit subscript $i$ for some reasons in \autoref{sub:schedule_the_jobs_in_machine}.

@@

\subsection{Provider schedule the jobs in machine} % (fold)
\label{sub:schedule_the_jobs_in_machine}
In order to reduce the idle rate, provider will schedule the inactive jobs on their machines. Since the schedule in service is a single machine scheduling problem that not on  what we focus in this study, we only discuss the job scheduling in resource. Since the  resource capacity dominance feature of service-call, it's necessary to suspend service-call in inactive status until all the job before it in $\mathcal{L}_{k,\tau}$ are finished, at the meantime, all the job after service-call should be stay in inactive status until the service-call is finished, as shown in \autoref{fig:simplejoblist}, service-call likes partition plate in $\mathcal{L}_{k,\tau}$.  
\begin{figure}[htbp]
	\centering
	\resizebox{.7\textwidth}{!}{\input{figures/service-call}}
	\caption{Simple illustration for one $\mathcal{L}_{k,\tau}$}
	\label{fig:simplejoblist}
\end{figure}
Therefore, the we just need to schedule the tasks before the first service-call in $\mathcal{L}_{k,\tau}$ when one of the active job in $\mathcal{G}_{k,\tau}$ was finished at $\tau_0$, we denote the set of schedule task at this time as $\mathcal{L}^{(s)}_{k,\tau_0}$

Specifically, a simple instance with configuration \autoref{tab:simplejobconfiguration} and schedule chart \autoref{fig:scheduleChart} will elucidate the setting.
This instance makes some simplification in the subscript fields in order to emphasize the resource cooperation, all the job performance can only be started when all its parts are in semi-activate status, the shadow in the figure shows the waiting period between the status transition. Horizontal dotted line constrained the available capacity of the resource for the subsequent jobs. Each finish of service-call will make the horizontal dotted line lower and it will never get higher again unless the related service is repealed.

@@

In every single resource, a schedule is given by a vector of ideal finish times $\bm{f}^{(s)} = \left[f_1^{(s)}, f_2^{(s)},\dots,f^{s}_n\right]$,$n=\abs{\mathcal{L}^{(s)}_{k,\tau_0}\cup\mathcal{H}^{(s)}_{k,\tau_0}}$. Since the task in $\mathcal{L}^{(s)}_{k,\tau_0},\mathcal{H}^{(s)}_{k,\tau_0}$ and $\mathcal{G}_{k,\tau_0}$ may come from different orders, we here use the single uniform subscript $j$ to distinguish these tasks and their related variables, we ignore the type subscript $\alpha$ because all the job assigned here are already type matched. The schedule model is:

\begin{equation}
\min_{\forall\bm{f}^{(s)}}\left( \max_{j\in L^{(s)}}\left\{ f_j^{(s)} - r_j - p_j \right\} \right) \label{eq:scheduleaim}
\end{equation}
\begin{numcases}{\text{s.t.}}
L^{(s)} = \left\{j| t_{j}\in \mathcal{L}^{(s)}_{k,\tau_0}\cup\mathcal{H}^{(s)}_{k,\tau_0}\right\} & \label{eq:subscript}\\
f^{(s)}_h \le f_j^{(s)} - p_j & $h\in\mathcal{P}_j$,$j\in L^{(s)}$\label{eq:subsequence}\\
G^{(s)} = \left\{j' | t_{j'}\in \mathcal{G}_{k,\tau_0}\right\} & \label{eq:activesubscript}\\
f^{(s)}_j =  \tau_0 + re_j & $j\in G^{(s)}$ \label{eq:alreadydefined}\\
\sum_{j\in\left\{  j' |t_{j'} \in\mathcal{G}_{k,\tau}\right\}} q_j \le A_{k,\tau}& $\tau \ge \tau_0$ \label{eq:caplimitwithtime} \\
f^{(s)}_j \ge \tau_0 + p_j & $j\in L^{(s)}$ \label{eq:finishconstrain}
\end{numcases}

The schedule aim for each resource \autoref{eq:scheduleaim} is to minimum the maximum delay of jobs. \autoref{eq:subsequence} makes sure that all predecessors of each job finished before the job itself. \autoref{eq:alreadydefined} means that the finish time of activate job is determined. \autoref{eq:caplimitwithtime} makes sure the capacity restriction at every time period and \autoref{eq:finishconstrain} defines the extreme situation of the finish time.
Since \autoref{eq:caplimitwithtime} is a time dependent function, the schedule model cannot be
solved with mixed integer programming (MIP) techniques.

@@

\subsection{Metabolism mode} % (fold)
\label{sub:metabolism mode}
Metabolism mode is one extension on the original mode for platform operator to control the number of individual in the system by both restrict the arrival and eliminate the current members. As shown in \autoref{fig:metabolismmode}, 
\begin{figure}[htbp]
    \centering
    \resizebox{0.85\textwidth}{!}{\input{figures/metabolism}}
    \caption{Metabolism mode}
    \label{fig:metabolismmode}
\end{figure}
machine scarcity is the control variable that can be defined as $\sum_jq_{\alpha,ij} - \sum_kC_{k,\tau}$ for resource in type $\alpha$ and the sum of task minus the sum of service in each type.

>>>>

\subsubsection{Assumptions} % (fold)
\label{ssub:assumptions_nomenclature}
To scope our research, we make some assumptions as follows for the original mode, while in other extension, some of the assumptions will be modified.
\begin{compactitem}
\item Each single task should be assembled by its task-parts, and these parts should be processed simultaneously;
\item The quality of product is determined by the worst quality of the selected resource;
\item Resource are renewable that the available capacity will be return to when the process procedure finished;
\item Resource quality comply normal distribution with given mean and standard deviation by provider when registered;
\item Cooperate and process procedure cannot be interrupted;
\item Provider can only schedule task-parts in inactive status. 
\end{compactitem}

@@

$(i,j,k,l,\alpha)$. When in schedule procedure, we omit subscript $i$ for some reasons in \autoref{sub:schedule_the_jobs_in_machine}.

@@

\subsubsection{Provider schedule the jobs in machine} % (fold)
\label{sub:schedule_the_jobs_in_machine}
In order to reduce the idle rate, provider will schedule the inactive jobs on their machines. Since the schedule in service is a single machine scheduling problem that not on  what we focus in this study, we only discuss the job scheduling in resource. Since the  resource capacity dominance feature of service-call, it's necessary to suspend service-call in inactive status until all the job before it in $\mathcal{L}_{k,\tau}$ are finished, at the meantime, all the job after service-call should be stay in inactive status until the service-call is finished, as shown in \autoref{fig:simplejoblist}, service-call likes partition plate in $\mathcal{L}_{k,\tau}$.  
\begin{figure}[htbp]
	\centering
	\resizebox{.7\textwidth}{!}{\input{figures/service-call}}
	\caption{Simple illustration for one $\mathcal{L}_{k,\tau}$}
	\label{fig:simplejoblist}
\end{figure}
Therefore, we just need to schedule the tasks before the first service-call in $\mathcal{L}_{k,\tau}$ when one of the active job in $\mathcal{G}_{k,\tau}$ was finished at $\tau_0$, we denote the set of schedule task at this time as $\mathcal{L}^{(s)}_{k,\tau_0}$

Specifically, a simple instance with configuration \autoref{tab:simplejobconfiguration} and schedule chart \autoref{fig:scheduleChart} will elucidate the setting.
This instance makes some simplification in the subscript fields in order to emphasize the resource cooperation, all the job performance can only be started when all its parts are in semi-activate status, the shadow in the figure shows the waiting period between the status transitions. Horizontal dotted line constrained the available capacity of the resource for the subsequent jobs. Each finish of service-call will make the horizontal dotted line lower and it will never get higher again unless the related service is repealed.

@@

% In every single resource, a schedule is given by a vector of ideal finish times $\bm{f}^{(s)} = \left[f_1^{(s)}, f_2^{(s)},\dots,f^{(s)}_n\right]$,$n=\abs{\mathcal{L}^{(s)}_{k,\tau_0}\cup\mathcal{H}^{(s)}_{k,\tau_0}}$. Since the task in $\mathcal{L}^{(s)}_{k,\tau_0},\mathcal{H}^{(s)}_{k,\tau_0}$ and $\mathcal{G}_{k,\tau_0}$ may come from different orders, we here use the single uniform subscript $j$ to distinguish these tasks and their related variables, we ignore the type subscript $\alpha$ because all the job assigned here are already type matched. The schedule model is:

% \begin{equation}
% \min_{\forall\bm{f}^{(s)}}\left( \max_{j\in L^{(s)}}\left\{ f_j^{(s)} - r_j - p_j \right\} \right) \label{eq:scheduleaim}
% \end{equation}
% \begin{numcases}{\text{s.t.}}
% L^{(s)} = \left\{j| t_{j}\in \mathcal{L}^{(s)}_{k,\tau_0}\cup\mathcal{H}^{(s)}_{k,\tau_0}\right\} & \label{eq:subscript}\\
% f^{(s)}_h \le f_j^{(s)} - p_j & $h\in\mathcal{P}_j$,$j\in L^{(s)}$\label{eq:subsequence}\\
% G^{(s)} = \left\{j' | t_{j'}\in \mathcal{G}_{k,\tau_0}\right\} & \label{eq:activesubscript}\\
% f^{(s)}_j =  \tau_0 + re_j & $j\in G^{(s)}$ \label{eq:alreadydefined}\\
% \sum_{j\in\left\{  j' |t_{j'} \in\mathcal{G}_{k,\tau}\right\}} q_j \le A_{k,\tau}& $\tau \ge \tau_0$ \label{eq:caplimitwithtime} \\
% f^{(s)}_j \ge \tau_0 + p_j & $j\in L^{(s)}$ \label{eq:finishconstrain}
% \end{numcases}

% The schedule aim for each resource \autoref{eq:scheduleaim} is to minimum the maximum delay of jobs. \autoref{eq:subsequence} makes sure that all predecessors of each job finished before the job itself. \autoref{eq:alreadydefined} means that the finish time of activate job is determined. \autoref{eq:caplimitwithtime} makes sure the capacity restriction at every time period and \autoref{eq:finishconstrain} defines the extreme situation of the finish time.
% Since \autoref{eq:caplimitwithtime} is a time dependent function, the schedule model cannot be
% solved with mixed integer programming (MIP) techniques.

@@

\subsection{Metabolism mode} % (fold)
\label{sub:metabolism mode}
Metabolism mode is one extension on the original mode for platform operator to control the number of individual in the system by both restrict the arrival and eliminate the current members. As shown in \autoref{fig:metabolismmode}, 
\begin{figure}[htbp]
    \centering
    \resizebox{0.85\textwidth}{!}{\input{figures/metabolism}}
    \caption{Metabolism mode}
    \label{fig:metabolismmode}
\end{figure}
we can define machine scarcity as $\sum_jq_{\alpha,ij} - \sum_kC_{k,\tau}$.

### 2016-09-08 result.tex
draft for cfp

\subsection{Experiments} % (fold)
\label{ssub:case_design}
We use the RanGen\cite{Demeulemeester2003} to generate order dataset in the well-known Patterson format with the parameters setting listed in \autoref{tab:generalparameter}. 
\begin{table}[htbp]
  \centering
  \scriptsize
  \caption{Order generating parameters setting}
    \begin{tabular}{cccccccccc}
    \toprule
    \textbf{$n_a$} & \textbf{OS} & \textbf{CI} & \textbf{$n_r$} & \textbf{RF} & \textbf{RC} & \textbf{$\lambda_d$} &\textbf{$\lambda_p$} & \textbf{$C_{k,0}$}\\
    \midrule
     10  &   0.3    &  [2,3]     &   12     &  0.3     &   0.5  & 0.2 & 0.3  & [20,30] \\
    \bottomrule
    \end{tabular}%
    {\footnotetext{\tiny The meaning of the first 5 parameters are defined in \cite{Demeulemeester2003}, $\lambda$ is the parameters of the arrival of user in simulation, $C_{k,0}$ is the initial capacity for $mr_k$}
    }
  \label{tab:generalparameter}%
\end{table}%
We assume provider and demander are arriving as the poisson process, in order to make sure the coming need resource capacity rate will not exceed the coming resource capacity rate in average to prevent the task explosion, we make sure that:
\begin{equation}
\lambda_d n_a n_r \cdot RF \cdot RC < \lambda_p \bar C_{k,0} \label{eq:balance}
\end{equation}

We design experiments in groups to validate incubation, outsourcing and metabolism mode \autoref{tab:grouping}, 10 datasets represent 10 types of orders, each of them contains 10 tasks with different configuration on 12 types of resources to perform with.

@@

\subsection{Result and analysis} % (fold)
\label{ssub:result_and_analysis}
Experiment on each mode in one group are simulated with same random seed to make no difference on the coming of order, provider and other irrelevant configuration to our validation.  After bunch of experiments with different random seeds, take random seed 776189616 as example, we run the simulation for 6000 tick time and the experiment's results are displayed in \autoref{fig:out} and \autoref{tab:averagevalue},
\begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth]{Data/out.pdf}
    \caption{Observed variable change with time}
    \label{fig:out}
\end{figure}
\begin{table}[htbp]
    \caption{Average observed values}
    \label{tab:averagevalue}
    \centering
    \scriptsize
    \begin{tabular}{lccccc}
    \toprule
    \textbf{Mode} & $\bar N_T$ & $\bar N_F$ & $\bar N_P$ & $\bar N_R $ & $\bar Q$\\
    \midrule
    Mode 11 & 1159.36 &  1644.201 &  1177.601 &  2053.727 &  8.388\\
    Mode 21 & \textit{636.769} &  \textit{2031.215} &  \textbf{692.716} &  \textbf{1066.947} &  16.016\\
    Mode 31 & 779.413 &  1996.021 &  \textit{782.272} &  \textit{1203.748} &  15.174\\
    Mode 12 & 1439.831 &  1522.923 &  1797.883 &  2954.113 &  14.057\\
    Mode 22 & \textbf{343.444} &  \textbf{2464.407} &  1316.952 &  1957.226 &  \textit{20.251}\\
    Mode 32 & 1164.409 &  1907.011 &  1597.742 &  2428.155 &  \textbf{20.652}\\

    \bottomrule
    \end{tabular}
\end{table}
we find: \begin{asparaenum}[1)]
\item Most dotted lines are above the full lines with the same series in $N_R,N_P,N_T$ means that metabolism mode need lower number of provider and resource, with the price of higher number of queue length of the tasks in resources in the system to deal with the same amount of needs, except for Mode 22. Full lines are not much above dotted lines in $N_F$ means that task finish rate will be a little lower with the metabolism, exception also appears in Mode 22. 
\item $L$ and $N_T$ both represent the job queue length, triangle and square line turned lower in $L$ meas that incubation mode can help reduce the waiting of job, these two type of line above the circle line means the incubation mode do reduce the resource idle rate.
\item Triangle lines are a little above the square lines in $N_R,N_P,N_T$ means that outsourcing mode needs more resources to operate and can only reduce the job queue length a little.
\item There is no big difference among all the 6 modes in rank change. Provider in metabolism mode will get lower rank value for they cannot stay in the system for a longer time to get higher rank value. Provider in Mode 11 even will not promote their rank value, which means that the metabolism rate is very fast if without incubation mode.
\item Mode 22 is a very special mode that reached the balance within 6000 ticks, that the number of provider and resource changes little with time goes by. Because our experiment setting comply \autoref{eq:balance}, the coming need capacity rate is lower than the coming capacity rate, Mode 12,22,32 will finally reach balance in the long run theoretically, but the appearance of service-call and metabolism mode itself is full of uncertainty, thus it's hard to predict when other metabolism related mode will reach the balance.
\item With the average data value shown in \autoref{tab:averagevalue}, metabolism with incubation but not with outsourcing mode is one ideal combine mode to maintain the system, resource will self-configured and controlled to justly meet the task need.
\end{asparaenum}

>>>>

\subsection{Experiments} % (fold)
\label{ssub:case_design}
We use the RanGen\cite{Demeulemeester2003} to generate order dataset in the well-known Patterson format with the parameters setting listed in \autoref{tab:generalparameter}. 
\begin{table}[htbp]
  \centering
  \scriptsize
  \caption{Order generating parameters setting}
    \begin{tabular}{cccccccccc}
    \toprule
    \textbf{$n_a$} & \textbf{OS} & \textbf{CI} & \textbf{$n_r$} & \textbf{RF} & \textbf{RC} & \textbf{$\lambda_d$} &\textbf{$\lambda_p$} & \textbf{$C_{k,0}$}\\
    \midrule
     10  &   0.3    &  [2,3]     &   12     &  0.3     &   0.5  & 0.2 & 0.3  & [20,30] \\
    \bottomrule
    \end{tabular}%
    {\footnotetext{\tiny The meaning of the first 5 parameters are defined in \cite{Demeulemeester2003}, $\lambda$ is the parameters of the arrival of user in simulation, $C_{k,0}$ is the initial capacity for $mr_k$}
    }
  \label{tab:generalparameter}%
\end{table}%
We assume provider and demander are arriving as the Poisson process, in order to make sure the coming need resource capacity rate will not exceed the coming resource capacity rate in average to prevent the task explosion, and we make sure that:
\begin{equation}
\lambda_d n_a n_r \cdot RF \cdot RC < \lambda_p \bar C_{k,0} \label{eq:balance}
\end{equation}

We design experiments in groups to validate incubation, outsourcing and metabolism mode \autoref{tab:grouping}, 10 datasets represent 10 types of orders, and each of them contains 10 tasks with different configuration on 12 types of resources to perform with.

@@

\subsection{Result and analysis} % (fold)
\label{ssub:result_and_analysis}
Experiment on each mode in one group are simulated with same random seed to make no difference on the coming of order, provider and other irrelevant configuration to our validation.  After bunch of experiments with different random seeds, take random seed 776189616 as example, we run the simulation for 6000 tick time and the experiment's results are displayed in \autoref{fig:out} and \autoref{tab:averagevalue},
\begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth]{Data/out.eps}
    \caption{Observed variable change with time}
    \label{fig:out}
\end{figure}
\begin{table}[htbp]
    \caption{Average observed values}
    \label{tab:averagevalue}
    \centering
    \scriptsize
    \begin{tabular}{lccccc}
    \toprule
    \textbf{Mode} & $\bar N_T$ & $\bar N_F$ & $\bar N_P$ & $\bar N_R $ & $\bar Q$\\
    \midrule
    Mode 11 & 1159.36 &  1644.201 &  1177.601 &  2053.727 &  8.388\\
    Mode 21 & \textit{636.769} &  \textit{2031.215} &  \textbf{692.716} &  \textbf{1066.947} &  16.016\\
    Mode 31 & 779.413 &  1996.021 &  \textit{782.272} &  \textit{1203.748} &  15.174\\
    Mode 12 & 1439.831 &  1522.923 &  1797.883 &  2954.113 &  14.057\\
    Mode 22 & \textbf{343.444} &  \textbf{2464.407} &  1316.952 &  1957.226 &  \textit{20.251}\\
    Mode 32 & 1164.409 &  1907.011 &  1597.742 &  2428.155 &  \textbf{20.652}\\

    \bottomrule
    \end{tabular}
\end{table}
we find: \begin{asparaenum}[1)]
\item Most dotted lines are above the full lines with the same series in $N_R,N_P,N_T$ means that metabolism mode need lower number of provider and resource, with the price of higher number of queue length of the tasks in resources in the system to deal with the same amount of needs, except for Mode 22. Full lines are not much above dotted lines in $N_F$ means that task finish rate will be a little lower with the metabolism, exception also appears in Mode 22. 
\item $L$ and $N_T$ both represent the job queue length, triangle and square line turned lower in $L$ means that incubation mode can help reduce the waiting of job, these two type of line above the circle line means the incubation mode do reduce the resource idle rate.
\item Triangle lines are a little above the square lines in $N_R,N_P,N_T$ means that outsourcing mode needs more resources to operate and can only reduce the job queue length a little.
\item There is no big difference among all the 6 modes in rank change. Provider in metabolism mode will get lower rank value for they cannot stay in the system for a longer time to get higher rank value. Provider in Mode 11 even will not promote their rank value, which means that the metabolism rate is very fast if without incubation mode.
\item Mode 22 is a very special mode that reached the balance within 6000 ticks, that the number of provider and resource changes little with time goes by. Because our experiment setting comply \autoref{eq:balance}, the coming need capacity rate is lower than the coming capacity rate, Mode 12,22,32 will finally reach balance in the long run theoretically, but the appearance of service-call and metabolism mode itself is full of uncertainty, thus it's hard to predict when other metabolism related mode will reach the balance.
\item With the average data value shown in \autoref{tab:averagevalue}, metabolism with incubation but not with outsourcing mode is one ideal combine mode to maintain the system, resource will self-configured and controlled to justly meet the task need.
\end{asparaenum}

### 2016-09-08 review.tex
draft for cfp

Simulation approach have been widely use in manufacturing system on operations planning and scheduling, real-time control, operating polities, performance analysis\cite{Smith2003}. In operating policies field, scheduling policies can be tested with simulation performance under given machine conditions\cite{Sabuncuoglu2003}, machine
segmentation policies can be simulated in a combined MRP and Kanban production system\cite{Felberbauer9-12Dec.2012}. Mourtzis et al.\cite{Mourtzis2015} explored a series of simulation-based solutions in industrial practice and considered that research trends are Internet and cloud based situation.

>>>>

Simulation approach have been widely used in manufacturing system on operations planning and scheduling, real-time control, operating polities, performance analysis\cite{Smith2003}. In operating policies field, scheduling policies can be tested with simulation performance under given machine conditions\cite{Sabuncuoglu2003}, machine
segmentation policies can be simulated in a combined MRP and Kanban production system\cite{Felberbauer9-12Dec.2012}. Mourtzis et al.\cite{Mourtzis2015} explored a series of simulation-based solutions in industrial practice and considered that research trends are Internet and cloud based situation.
